\documentclass{article}

\begin{document}

\author{Dustin Neumann}
\title{SkyVault Design Document}
\date{1/12/2019}
\maketitle

\section{Abstract}
SkyVault is a passion project for me

\section{Story} 

\subsection{Characters}
\subsection{Plot}

\subsubsection{Ideas}
Ideas:
The characters boyfriend is the one that created the virus

\begin{bfseries}
    Timeline
\end{bfseries}


1. Exposition
2. Inciting Incident
    2.1 Conflict 1: How does she respond?

3. Rising
4. Distaster
5. Climax

\subsubsection{Main Idea}
In the world there is a virus, and people carry many different strains of this virus. This virus was constructed by a device called the `Terminal'.

Our main character is a plague doctors apprentice.

You walk into a house, you see a man over a woman, the man is covered in blood, the woman is clearly dead. The man looks up and leaps at you. You enter combat, if you heal the man, he comes back to sanity, and sees what happened, we morns over the body.

\subsubsection{Scene 1}


\subsection{Ending} 

\section{Gameplay} 

\subsection{Combat} 
The combat is a lot like Paper Mario, but with a twist, so our goal is not to kill the monster, but instead cure it. So the player will have main attacks, but they will be quite powerful and will do pleanty of damage. The challenge comes from the player using different cures against the enemy. Each cure will have a difficult mini game.

\subsection{Overworld}

\subsubsection{Main Island}
Southern forest / Medow

\subsection{Interactions}
\subsubsection{Dialog}
\subsubsection{Menus} 

\section{Art}

\section{Sound Design}

\end{document}
